My title

### 2024-03-10 paper/paper.qmd
added here::here to the readr function, previous issue is fixed

## Helpline Wrap-Up Codes Data
```{r}
#| label: tbl-monthly-coded
#| tbl-cap: Sample of monthly summation for Helpline Coded Calls data
#| echo: false

cleaned_data <- read_parquet("data/analysis_data/cleaned_data.parquet")

@@

knitr::kable(sample_helpline, col.names = c("Month", "Calls Coded", "Referral to Shelter", "Homelessness Prevention Info"), align = c("l", "c", "c", "c"))
```

## Final Combined Dataset
```{r}
#| label: tbl-monthly-calls
#| tbl-cap: Sample of monthly homeless death count and Helpline Coding efforts
#| echo: false

>>>>

## Central Intake Call Wrap-Up Codes
```{r}
#| label: tbl-monthly-coded
#| tbl-cap: Sample of monthly summation for Helpline Coded Calls data
#| echo: false

cleaned_data <- read_parquet(here::here("data/analysis_data/cleaned_data.parquet"))

@@

knitr::kable(sample_helpline, col.names = c("Month", "Calls Coded", "Referral to Shelter", "Homelessness Prevention Info"), align = c("l", "c", "c", "c"))
```
## Deaths of People Experiencing Homelessness

```{r}
#| label: tbl-death-count
#| tbl-cap: Sample of Cleaned Deaths of People Experiencing Homelessness Dataset
#| echo: false

sample_death_counts <- cleaned_data |> select(Month_date, Death_Count)

sample_death_counts <- head(sample_death_counts)

knitr::kable(sample_death_counts, col.names = c("Month", "Death Count"), align = c("c", "c"))
```

## Final Combined Dataset
```{r}
#| label: tbl-combined
#| tbl-cap: Sample of monthly homeless death count and Helpline Coding efforts
#| echo: false
